MS797 Glossary

### 2022-02-28 _academics/ms797-glossary/ms797-glossary.Rmd
knit and clean build

variance (34)
: _"the amount by which $\hat{f}$ would change if we estimated it using a different training data set"_

>>>>

variance (34)
: _"the amount by which $\hat{f}$ would change if we estimated it using a different training data set"_
More practically: the *average* of squared differences from the mean, often expressed as $\sigma^2$, where $\sigma$ (or the square root of the variance) is the standard deviation
